Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes

### 2018-11-17 Ben_Manuscripts/structure_paper/supporting_information.tex
Working on response to reviewers

  We chose to build all systems using 20 monomers per column, i.e. for a simulation with 5 columns around each pore, there are 100 monomers per pore, and 400 monomers per simulation.  We made this choice
  by considering a number of factors that directly affect the quality of our results. 
  Clearly, choosing a smaller number of layers will cause the system to suffer from 
  larger finite size effects. Even in our 20 monomer-per-column system, axial correlations
  between stacked monomers persist throughout the entire correlation function (see
  Figure~\ref{M-fig:correlation} of the main text). The correlation function of the system which we
  built with 40 monomers per column is very similar to that created with 20 monomers
  per columns (continues to oscillate for its full length
  (Figure~\ref{fig:tall_correlation_full})). If we continue adding monomers, the 
  correlation function will eventually fully decay but it is not worth the 
  computational expense. We do find that the correlation lengths calculated from 20
  monomer per column simulations are in sufficient agreement with experiment.

@@

@@

  In Section~\ref{M-section:slow_dynamics} of the main text, we calculated the
  autocorrelation function of the outer tail either dihedrals pictured
  in Figure~\ref{fig:dihedrals}.

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{monomer_dihedrals.png}
  \caption{We measured the autocorrelation functions of the dihedrals highlighted in
  black. We only included dihedrals associated with the outer tails in our calculation
  since the position of the center tail leads to fundamentally different interactions and
  dynamics.}\label{fig:dihedrals}
  \end{figure}

>>>>

  We chose to build all systems using 20 monomers per column, i.e. for a simulation with 5 
  columns around each pore, there are 100 monomers per pore, and 400 monomers per simulation.  We made this choice
  by considering a number of factors that directly affect the quality of our results. 
  Clearly, choosing a smaller number of layers will cause the system to suffer from 
  larger finite size effects. Even in our 20 monomer-per-column system, axial correlations
  between stacked monomers persist throughout the entire correlation function (see
  Figure~\ref{fig:correlation}). The correlation function of the system which we
  built with 40 monomers per column is very similar to that created with 20 monomers
  per column (it continues to oscillate for its full length
  (Figure~\ref{fig:tall_correlation_full})). If we continue adding monomers, the 
  correlation function will eventually fully decay but it is not worth the 
  computational expense. We do find that the correlation lengths calculated from 20
  monomer per column simulations are in sufficient agreement with experiment.

@@

  \section{Correlation Functions}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich.pdf}
  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset.pdf}
  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.pdf}
  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.pdf}
  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
  \end{subfigure}  
  \caption{1D correlation functions of the center of masses of aromatic head
	  groups, $g(z)$, show decaying oscillatory behavior and have consistent
	  correlation lengths with experiment. We calculated the correlation length by
	  fitting a decaying exponential function
	  (Equation~\ref{M-eqn:decaying_exponential} of the main text) to the peaks of $g(z)$. The
	  correlation length is longer for ordered basin systems
	  (Table~\ref{M-table:correlation_length} of the main text). We did not attempt to calculate the
	  correlation length for (d) because there are no clear peaks. We assume that
	  this correlation length is less than the vertical distance between
	  monomers.}\label{fig:correlation}
  \end{figure}

  \section{Structure factors of simplified systems}\label{section:simplified_sf}

  In the Section~\ref{M-section:rpi} of the main text, we used simplified systems
  made up of point scatterers in order to understand the main factors that influence
  the cross-sections of R-$\pi$. We showed that both the shape and the intensity
  of R-$\pi$ are strongly influenced by the degree of correlation between columns.
  Here we show the influence of varied amounts of noise on the $xy$ plane and in
  the $z$-direction for select cases.

  Increasing thermal noise in the $z$-direction will reduce the intensity
  of R-$\pi$, however the $q_r$ profile remains unchanged. When we increased the
  thermal noise of the simplified parallel displaced system with fully correlated
  columns in the $z$-direction by 12\% and 27\%, we saw a 3 and 15-fold decrease in
  the maximum intensity of R-$\pi$ respectively (Figure~\ref{fig:intensity_vs_zsigma}).
  Despite the decrease in intensity, the 3 cross-sections have the same shape 
  (Figure~\ref{fig:rpi_xsection_vs_zsigma}), whose sharp Bragg-like peaks are
  not consistent with experiment.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{intensity_vs_zsigma.pdf}
  \caption{}\label{fig:intensity_vs_zsigma}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.pdf}
  \caption{}\label{fig:rpi_xsection_vs_zsigma}
  \end{subfigure}
  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
  thermal noise in the $z$-direction; however, the $q_r$ cross-section profile does
  not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
  $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the
  background intensity, relative to systems with simulation levels of disorder (blue)
  by a factor of 3 when we increase $\sigma_z$ by 12\% (green) and by a factor 
  of 15 when we increase $\sigma_z$ by 27\% (red). (b) Although the maximum intensity of R-$\pi$
  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
  \end{figure}

  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
  cross-section of R-$\pi$ to, somewhat counterintuitively, decrease. Using a
  system with uncorrelated columns, we modified the disorder in both the $r$ and
  $\theta$ directions by multiplying their values by a factor of 0.5 and 2
  (Figure~\ref{fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
  by 88\%. When we double the noise, the FWHM decreases by 51\%. As we have fit
  the data in Figure~\ref{fig:sim_rsection_fit}, the FWHM of R-$\pi$ agrees well
  with experiment, meaning the quenched configuration contains about the right
  amount of disorder on the $xy$ plane. However, the relatively low quality of
  the fit implies that the FWHM of a fixed Lorentzian fit to data from a single
  simulation might not be the best comparison to experiment and that some form of
  initial configuration dependence causes extra structure.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{qy_fwhm.pdf}
  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
	  FWHM of the $q_r$ cross-section of R-$\pi$. When we cut the amount of $r$ and
	  $\theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
	  we double the disorder (Noise factor = 2), the FWHM decreases by
	  51\%.}\label{fig:qy_fwhm}
  \end{figure}

@@

  In Section~\ref{M-section:slow_dynamics} of the main text, we calculated the
  autocorrelation function of the outer tail either dihedrals pictured
  in Figure~\ref{fig:dihedral_illustration}. The plots of the autocorrelation
  functions versus time lag are shown in Figure~\ref{fig:dihedral}.

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{monomer_dihedrals.png}
  \caption{We measured the autocorrelation functions of the dihedrals highlighted in
  black. We only included dihedrals associated with the outer tails in our calculation
  since the position of the center tail leads to fundamentally different interactions and
  dynamics.}\label{fig:dihedral_illustration}
  \end{figure}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  	\centering
  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_300K.pdf}
  	\caption{300K}\label{fig:dihedrals_300K}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  	\centering
  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_500K.pdf} % Run : torsions.py -t tethered_columns.xtc -g tethered_columns.gro (the appropriate dihedral is the default)
  	\caption{500K}\label{fig:dihedrals_500K}
  \end{subfigure}
  \caption{The outer tail ether dihedrals become decorrelated on a reasonable
  timescale when we raise the system temperature. (a) The dihedrals do not
  become decorrelated for ca. 100 ns when the system is equilibrated at 300 K.
  (b) The ether dihedrals become decorrelated after 11 ns when the temperature
  of the system is increased to 500 K.}\label{fig:dihedral}
  \end{figure}
